Data_Analysis_MS_ddm_exp1

### 2018-07-10 Results/preproc/MS_ddm_preproc.rmd
revise the cross-task analysis of study 1

# calculate the effect of self-ref and valence
df.M1.v.sum_eff_w <- df.M1.V.sum_w[,1:3]
df.M1.v.sum_eff_w$d_Good_Self_Other <- df.M1.V.sum_w$d_Good_Self - df.M1.V.sum_w$d_Good_Other
df.M1.v.sum_eff_w$d_Self_Good_Bad   <- df.M1.V.sum_w$d_Good_Self - df.M1.V.sum_w$d_Bad_Self

df.M1.v.sum_eff_w$RT_Good_Self_Other <- df.M1.V.sum_w$RT_match_Good_Other -  df.M1.V.sum_w$RT_match_Good_Self
df.M1.v.sum_eff_w$RT_Self_Good_Bad   <- df.M1.V.sum_w$RT_match_Bad_Self -  df.M1.V.sum_w$RT_match_Good_Self

@@

# combine data cross task
# tmp <- aggregate(df.C1.V.acc[,7],list(df.C1.V.acc$Subject,df.C1.V.acc$Morality,df.C1.V.acc$Identity),mean)
#df.C1.V.acc.noTask <- summarySE(df.C1.V.acc,measurevar = 'ACC',groupvars = c('Subject','Morality','Identity'))
#df.C1.V.acc.noTask_w <- dcast(df.C1.V.acc.noTask, Subject ~  Morality + Identity  ,value.var = "ACC")

df.C1.V.acc_noTask_w$good_bad_slf <- df.C1.V.acc_noTask_w$ACC_Good_Self - df.C1.V.acc_noTask_w$ACC_Bad_Self
df.C1.V.acc_noTask_w$good_bad_oth <- df.C1.V.acc_noTask_w$ACC_Good_Self - df.C1.V.acc_noTask_w$ACC_Bad_Other
df.C1.V.acc_noTask_w$slf_oth_good <- df.C1.V.acc_noTask_w$ACC_Good_Self - df.C1.V.acc_noTask_w$ACC_Good_Other
df.C1.V.acc_noTask_w$slf_oth_bad <- df.C1.V.acc_noTask_w$ACC_Bad_Self - df.C1.V.acc_noTask_w$ACC_Bad_Other

@@

df.C1.v.sum_eff_w$ACC_Val_Good_selfEffect <- df.C1.V.sum_w$ACC_Val_Good_Other - df.C1.V.sum_w$ACC_Val_Good_Self
df.C1.v.sum_eff_w$ACC_Val_Self_valEffect  <- df.C1.V.sum_w$ACC_Val_Bad_Self - df.C1.V.sum_w$ACC_Val_Good_Self
df.C1.v.sum_eff_w$ACC_Id_Good_selfEffect  <- df.C1.V.sum_w$ACC_Id_Good_Other - df.C1.V.sum_w$ACC_Id_Good_Self
df.C1.v.sum_eff_w$ACC_Id_Self_valEffect   <- df.C1.V.sum_w$ACC_Id_Bad_Self - df.C1.V.sum_w$ACC_Id_Good_Self

>>>>

# calculate the effect of self-ref and valence
df.M1.v.sum_eff_w <- df.M1.V.sum_w[,1:3]
df.M1.v.sum_eff_w$d_Good_selfEffect <- df.M1.V.sum_w$d_Good_Self - df.M1.V.sum_w$d_Good_Other
df.M1.v.sum_eff_w$d_Self_valEffect   <- df.M1.V.sum_w$d_Good_Self - df.M1.V.sum_w$d_Bad_Self

df.M1.v.sum_eff_w$RT_Good_selfEffect <- df.M1.V.sum_w$RT_match_Good_Other -  df.M1.V.sum_w$RT_match_Good_Self
df.M1.v.sum_eff_w$RT_Self_valEffect   <- df.M1.V.sum_w$RT_match_Bad_Self -  df.M1.V.sum_w$RT_match_Good_Self

@@

# calculate the mean differences(?)
df.C1.V.acc_noTask_w$good_bad_slf <- df.C1.V.acc_noTask_w$ACC_Good_Self - df.C1.V.acc_noTask_w$ACC_Bad_Self
df.C1.V.acc_noTask_w$good_bad_oth <- df.C1.V.acc_noTask_w$ACC_Good_Self - df.C1.V.acc_noTask_w$ACC_Bad_Other
df.C1.V.acc_noTask_w$slf_oth_good <- df.C1.V.acc_noTask_w$ACC_Good_Self - df.C1.V.acc_noTask_w$ACC_Good_Other
df.C1.V.acc_noTask_w$slf_oth_bad <- df.C1.V.acc_noTask_w$ACC_Bad_Self - df.C1.V.acc_noTask_w$ACC_Bad_Other

@@

df.C1.v.sum_eff_w$ACC_Val_Good_selfEffect <- df.C1.V.sum_w$ACC_Val_Good_Self - df.C1.V.sum_w$ACC_Val_Good_Other
df.C1.v.sum_eff_w$ACC_Val_Self_valEffect  <- df.C1.V.sum_w$ACC_Val_Good_Self - df.C1.V.sum_w$ACC_Val_Bad_Self
df.C1.v.sum_eff_w$ACC_Id_Good_selfEffect  <- df.C1.V.sum_w$ACC_Id_Good_Self - df.C1.V.sum_w$ACC_Id_Good_Other
df.C1.v.sum_eff_w$ACC_Id_Self_valEffect   <- df.C1.V.sum_w$ACC_Id_Good_Self - df.C1.V.sum_w$ACC_Id_Bad_Self
